Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining

### 2015-11-08 2_relatedwork/relatedwork.tex
no message

Cross-organizational mining is based on cross-correlation of workflows and the realized activities in different organization to compare in an objective approach. In the study of Bujis et al. \cite{buijs2012towards}, process models and behaviors of organizations are cross-compared with the idea of supporting and representing. In the studies of van der Aalst \cite{van2011business,van2011intra}, configurable process models are proposed with the ideas of \textit{exploiting commonality} and \textit{collaboration} for the organizations sharing the same infrastructure and doing the similar work. In this study, usage of cross-organizational process mining is based on \textit{exploiting commonality} where organizations can learn from each other.

>>>>

Cross-organizational mining is based on cross-correlation of workflows and the realized activities in different organization to compare in an objective approach. In the study of Buijs et al. \cite{buijs2012towards}, process models and behaviors of organizations are cross-compared with the idea of supporting each other and representing differences. In the studies of van der Aalst \cite{van2011business,van2011intra}, configurable process models are proposed with the ideas of \textit{exploiting commonality} and \textit{collaboration} for the organizations sharing the same infrastructure and doing the similar work. In this study, usage of cross-organizational process mining is based on \textit{exploiting commonality} where organizations can learn from each other.
